---
title: "Tidy08"
author: "Sandy Illescas"
date: "2023-06-04"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(
	message = FALSE,
	root.dir = "~/Users/SandyCruz/Desktop/Repositories/Illescas_Tidy_Tuesdays",
  fig.path = "Output/",
	warning = TRUE,
	include = TRUE
)
```


# Load Libraries
```{r}
library(dplyr)
library(ggplot2)
library(ggthemes)

```


# Load Dataset
```{r}

age_gaps <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-02-14/age_gaps.csv')

```

# Organize and Filter Data
```{r}

age_diff_avg <- age_gaps %>% #creating a new dataset to work with
  group_by(character_1_gender, character_2_gender) %>% # this allows us to group based on main character gender
  summarise(avg_age_diff = mean(age_difference, na.rm = TRUE)) #this allows us to take the mean for each group

```

# Create Graph
I wanted to create a graph showing the differnce in age difference between the main character "couples" dependant on wether the MAIN character was a man or a woman.  What this graph shows, that in movies where the MAIN character is a man, there are more cases where the age difference is larger compared to when a woman is the MAIN character.  This shows us that when women are the MAIN character, there are more instances where the age gap is smaller.  I thought a violin plot would be a good tool to practice and also is able to help us visualize the distribution among the two groups. 
```{r}
ggplot(age_gaps, aes(x = factor(character_1_gender), y = age_difference, fill = factor(character_1_gender))) + # this allows us to create a graph to compaare the age difference of age gap between the two groups
  geom_violin() + # this allows us to chage our plot to a violin type plot
  labs(x = "Main Character Gender", y = "Age Difference",
       title = "Age Difference of Couples Based on Main Character Gender") + # this allow us to change the titles to the x-axis, y-axis, and the main graph title
  scale_fill_discrete(name = NULL) + #this allows us choose to not name the legend since it is unnecessary 
  theme_clean()+ # This gives us a cleaner graph with dotted lines
  theme(legend.position = "none", plot.title = element_text(size = 15, face = "bold")) # this allows us to not include the legend, change the plot title size, and also make it bold

```

