---
title: "Tidy02"
author: "Sandy Illescas"
date: "2023-05-11"
output: 
  html_document

---

```{r setup, include=FALSE}

knitr::opts_chunk$set(
	message = FALSE,
	root.dir = "~/Users/SandyCruz/Desktop/Repositories/Illescas_Tidy_Tuesdays",
  fig.path = "Output/",
	warning = TRUE,
	include = FALSE
)
```


### Load Libraries

```{r, include=TRUE, echo=TRUE}

library(readr)
library(dplyr)
library(ggplot2)
library(reticulate)

```


### Load Data

```{r, echo=TRUE, include=TRUE}

babynames <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-03-22/babynames.csv')

```

## I was actually having a difficult time with the data so instead of wasting time I followed a promt to create my ownd data, so that was really fun.


## Create Example Data Frame

```{r, echo=TRUE, include=TRUE}

df <- data.frame(name = c("Emma", "Olivia", "Ava", "Isabella", "Sophia", "Mia", "Charlotte", "Amelia", "Harper", "Evelyn", "Liam", "Noah", "William", "James", "Oliver", "Benjamin", "Elijah", "Lucas", "Mason", "Logan"),
                 sex = c(rep("F", 10), rep("M", 10)),
                 count = c(20355, 19529, 16237, 15527, 15158, 14365, 13191, 13074, 12816, 12537, 18696, 17718, 16752, 15688, 14687, 14569, 14277, 14077, 13579, 13489))

```



### Here I organized the in a way that made sense and would be easier to plot

```{r, include=TRUE}


top10_names <- df %>% # group data by name and sex, and calculate total count for each group
  group_by(name, sex) %>% 
  summarize(n = sum(count)) %>% 
  ungroup() %>% 
  arrange(sex, desc(n)) %>% 
  group_by(sex) %>% 
  top_n(10)

```

### Now that our data is ready, we can make a graph.
#### I chose this graph mainly to remind myself that flipping the coordinates can be done easily if your data set isn't too complicated

## Top 10 Names by Sex
```{r, echo=TRUE, include=TRUE}

p1 <- ggplot(top10_names, aes(x = reorder(name, n), y = n, fill = sex)) + # now we can  top 10 names by sex
  geom_col() + #column chart
  geom_text(aes(label = n), nudge_y = 2) + 
  coord_flip() + # swaps the coordinates so we can see it sideways
  scale_fill_viridis_d() +
  labs(title = "Top 10 Baby Names by Sex", x = "Name", y = "Total Count")

p1

```


### During our presentations someone put their values by their bars, but these numbers are so big, it doesnt' really make.  I personally found them more distracting than helpful, but they are easily removed...


## Same Graph, just not so annoying

```{r, echo=TRUE, include=TRUE}

p2 <- ggplot(top10_names, aes(x = reorder(name, n), y = n, fill = sex)) + # now we can  top 10 names by sex
  geom_col() + #column chart
  coord_flip() + # swaps the coordinates so we can see it sideways
  scale_fill_viridis_d() +
  labs(title = "Top 10 Baby Names by Sex", x = "Name", y = "Total Count")

p2


```

### My last graph for this was something that I sometimes struggle with too much color, so I made a graph represening the same data, but much easier on the eyes. 


```{r, echo=TRUE, include=TRUE}

p3 <- ggplot(top10_names, aes(x = name, y = n)) +
  geom_segment(
    aes(x = name, xend = name, y = 0, yend = n), 
    color = "lightgray"
    ) + 
  geom_point(aes(color = sex), size = 3) +
  scale_color_viridis_d() +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

p3



```



